Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
add some sources

There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management. Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
{\color {red} stats on pervasiveness of censorship here}
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

@@

Our hypothesis is that the average user does not have knowledge
knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
addresses bridges. Certain real-world censorship settings require the user to provide this
information during configuration, which will affect how successful users are at 
circumventing censorship using Tor. There are blogs in countries which have extensive
censorship on how to configure Tor correctly {\color {red} cite something}, and participants may 
receive additional informatio through word of mouth. Our study will measure if the configuration
interface successfully guides users to correctly configuring their browser, not accounting 
for any additional  information that a real user may have.\\

>>>>

There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management. Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
Internet censorship is shown to be pervasive across the world today \ref{faris2008measuring}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

@@

Our hypothesis is that the average user does not have knowledge
knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
addresses bridges. Certain real-world censorship settings require the user to provide this
information during configuration, which will affect how successful users are at 
circumventing censorship using Tor. Participants may receive additional information through word 
of mouth, help from relatives, or blogs. Our study will measure if the configuration
interface successfully guides users to correctly configuring their browser, not accounting 
for any additional  information that a real user may have.\\
